Foreground Detection via Deep Variation Transformation

### 2019-01-21 draft.tex
all done except the description of network architecture

\subsection*{Network Work Architecture and Variation Transformation}
% 先描述动机
As we mentioned above,
the main purpose of our DPVTL is trying to transform the sequence of pixels' observations 
into another space where the observations are easier classified.
% 分析问题，提出解决的方案，要用数学化的形式
Therefore,
our network entails learning a mapping from the input observations of pixels $s \in \mathcal{S}$ 
to the probability $p \in \mathcal{P}$ of the corresponding pixel belong to foreground or background,
and a end-to-end architecture network is proposed to transform the observations of pixels to a new space which is close to labels as shown in the \reffig{flow_chart}.
%
Mathematically, the training procedure is shown as follows:
\begin{equation}
    \begin{split}
        \mathcal{P}(m,n) & = f_{\theta_N} ( f_{\theta_{N - 1}} ( \cdots f_{\theta_1} ( \mathcal{S}(m,n)) \cdots  ) )  \\
          & = f_{ \prod_{n=1}^{N}\theta_n   }^n(\mathcal{S}(m,n)),
    \end{split}
\end{equation}
where $\mathcal{P}(x,y)$ is denoted as the probability, $\mathcal{S}(m,n)$ is the input patch of network and $f_{\theta_i}$ is represents different layers of network.
% where, $S'(m,n)$ is the prediction of the network, and the forward computation at each layer of the network is represented by $f_{\theta_N}$. The symmetric padding process is denoted as $Pad$, where we have lost none of the pixel information to make the output $S'(m,n)$ the same size as the pixel patch $S(m,n)$. 
% Another advantage of symmetric padding is that the order information still remains.

@@

The network used in this work is devised as an end-to-end architecture,

@@

\subsection{Foreground Detection}
%As shown in the \reffig{flow_chart}, 
Then, the prediction maps can be reconstructed from the prediction patches.
%
Then a global threshold $T_r$ is set for each transformed observation in order to map them to $\{0,1\}$. 
%
The threshold function is given by
\begin{equation}
    \label{piecewise_fg}
    g(x,y) =
 \begin{cases}
  1,  \quad x < y       \\
  0,  \quad otherwise   \\
\end{cases},
\end{equation}

\begin{equation}
    \mathcal{M}(x,y) = g(T_f, \mathcal{C}^{-1}(S'(x,y), R)),
\end{equation}
where the $M$ denotes the final foreground map given by our DPVTL model.
After the thresholding calculations, our experiment results show that a random initialized FCNs, trained end-to-end on feature learning can achieve the state-of-the-art without further machinery.

>>>>

\subsection*{Network Work Architecture and Variation Transformation}
% 先描述动机
As we mentioned above,
the main purpose of our DPVTL is the transformation between the sequence of pixels' observations with possibility of pixels belong to foreground or background.
% the main purpose of our DPVTL is trying to transform the sequence of pixels' observations 
% into another space where the observations are easier classified.
% 分析问题，提出解决的方案，要用数学化的形式
Therefore,
our network entails learning a mapping from the input observations of pixels $s \in \mathcal{S}$ 
to the probability $p \in \mathcal{P}$ of the corresponding pixel belong to foreground or background,
and a end-to-end architecture network is proposed to transform the observations of pixels to a new space which is close to labels as shown in the \reffig{flow_chart}.
%
Mathematically, the training procedure is shown as follows:
\begin{equation}
    \begin{split}
        \mathcal{P}(m,n) & = f_{\theta_N} ( f_{\theta_{N - 1}} ( \cdots f_{\theta_1} ( \mathcal{S}(m,n)) \cdots  ) )  \\
          & = f_{ \prod_{n=1}^{N}\theta_n   }^n(\mathcal{S}(m,n)),
    \end{split}
\end{equation}
where $\mathcal{P}(x,y)$ is denoted as the probability, $\mathcal{S}(m,n)$ is the input patch of network and $f_{\theta_i}$ is represents different layers of network.
% where, $S'(m,n)$ is the prediction of the network, and the forward computation at each layer of the network is represented by $f_{\theta_N}$. The symmetric padding process is denoted as $Pad$, where we have lost none of the pixel information to make the output $S'(m,n)$ the same size as the pixel patch $S(m,n)$. 
% Another advantage of symmetric padding is that the order information still remains.

@@

% 描述网络结构
The network used in this work is devised as an end-to-end architecture XXX
The structure of our FCN for foreground detection is shown in \reffig{flow_chart}. 
The proposed FCN contains 6 convolutional layers, and the last convolutional layer has a filter size of $1\times 1$. 
We use the Rectified Linear Unit (ReLU) as the activation function after each convolutional layer and the Sigmoid function after the last fully connected layer. 
We do not use any other tricks in our network training and the experiment results prove that the proposed approach is feasible and very effective.
After the thresholding calculations, our experiment results show that a random initialized FCNs, trained end-to-end on feature learning can achieve the state-of-the-art without further machinery. 
\todo{please giving a comprehensive description of the details about the network architecture.}

@@

\subsection{Foreground Detection}
%As shown in the \reffig{flow_chart}, 
After the transformation from observations to the probability belong to foreground or background,
the foreground is detected from the final binary mask.
%
During the transformation,
the pixel patches are feed into the network and transformed into the probability patches,
which are compared with a threshold $T_r$ for classification and then used to reconstruct the foreground for final results.
%
The comparison with threshold is mathematically shown as follows:
\begin{equation}
    \mathcal{M}(x,y) = g(T_f, \mathcal{C}^{-1}(S'(x,y), R)),
\end{equation}
where the $\mathcal{M}(x,y)$ is the final binary mask.
%
The $S'(x,y)$ is the probability patches output by the network,
the $\mathcal{C}^{-1}$ is the reversed procedure of the reshape procedure shown in the \refeq{eq_reshape} and $R$ is the parameter for the reversing procedure of reshape.
%
The $T_f$ is the threshold given by user and the $g()$ is the thresholding function which is shown as follows:
% Then the reverse procedure of \refeq{eq_reshape}
% 
% used to reconstruct the foreground image for the final results.
% %
% 
% 
% The network devised in proposed approach 
% 
% 
% Then, the prediction maps can be reconstructed from the prediction patches.
% %
% Then a global threshold $T_r$ is set for each transformed observation in order to map them to $\{0,1\}$. 
% %
% The threshold function is given by
\begin{equation}
    \label{piecewise_fg}
    g(x,y) =
 \begin{cases}
  1,  \quad x < y       \\
  0,  \quad otherwise   \\
\end{cases},
\end{equation}
%
%where the $M$ denotes the final foreground map given by our DPVTL model.
